### 2015-11-06 CVPR16/Source/intro.tex
changes
small changes in Intro & Related Work

As a 2D projection of the 3D world, image formation is often associated with a loss of information. This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint. In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion and object detection. However, occlusions still present a difficult challenge, with the difficulty of physically modeling them being a major bottleneck. 
%Prior works have considered occlusions in 2D or through discrete occluder patterns

@@

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for modeling the association of 3D structure from motion points with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.

@@

To summarize, our main contributions are:
\vspace{-0.2cm}
\begin{tight_itemize}
%\setlength\itemsep{0cm}
\item A novel theoretical model for handling occlusions that is continuous and 3D.
\item Unified occlusion handling in various applications, such as 3D points in SFM and bounding boxes in object detection.
\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
\end{tight_itemize}

>>>>

As a 2D projection of the 3D world, image formation is often associated with a loss of information. This is especially significant when objects in 3D space occlude each other with respect to the camera viewpoint. In recent years, we have seen remarkable progress in various fields that enable scene understanding, such as structure from motion (SFM) and object detection. However, occlusions still present a difficult challenge, with the difficulty of physically modeling them being a major bottleneck. 
%Prior works have considered occlusions in 2D or through discrete occluder patterns

@@

A key advantage afforded by our occlusion model is unification. While previous approaches to handling occlusion are application-dependent, ours is physically-inspired, thus, flexible enough to be used in a variety of scenarios. In this paper, we show that our theory can be used for modeling the association of 3D SFM points with static or dynamic objects (Section \ref{sec:association}), as well as modeling object detection scores in applications like 3D localization (Section \ref{sec:localization}). We demonstrate application of our formulations for road scenes from the KITTI dataset \cite{Geiger_etal_2012}.

@@

To summarize, our main contributions are:
\vspace{-0.2cm}
\begin{tight_itemize}
%\setlength\itemsep{0cm}
\item A novel theoretical model for handling occlusions that is continuous and formulated in 3D.
\item Unified occlusion handling in various applications, such as 3D points in SFM and bounding boxes in object detection.
\item Application of our model to association of point tracks with both static and moving objects, improving over motion segmentation and occlusion-unaware baselines.
\item Application of our unified formulation to 3D localization of traffic participants in road scenes.
\end{tight_itemize}

### 2015-11-06 CVPR16/Source/related.tex
small changes in Intro & Related Work

\vspace{-0.3cm}
\paragraph{Occlusion handling in tracking}
Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling, on the other hand, is fully 3D, based on physical modeling of object-ray intersections and much more general in determining the probability of a point in space as belonging to an object. While our model can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it has far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.

@@

\vspace{-0.3cm}
\paragraph{Motion segmentation and multibody SFM}
An application for our occlusion modeling is to determine point track associations in scenes with multiple objects. For moving objects, this is within the purview of motion segmentation, which has been approached through algebraic factorization methods \cite{Costeria98,Vidal03,Vidal04}, statistical methods~\cite{Kanatani01,Gruber04,Rao08} and clustering methods~\cite{Yan06,Goh07}. Some recent efforts include robust algebraic segmentation with hybrid perspective constraints \cite{Rao_etal_2010} and spectral clustering with point track spatial affinities \cite{Brox_Malik_2010}. In contrast to our modeling, such methods cannot handle static objects, or dynamic objects with little relative motion.
%\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 
Closer to our application, motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}. In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.

@@

\vspace{-0.3cm}
\paragraph{3D localization}
One of the vital goals of 3D scene understanding is to localize the 3D objects in complex scenes. 
%For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. 
Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} consider partial object detectors. A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects. In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space and derives unified representations for SFM points and object detection bounding boxes. This makes our model more general, extensible and amenable for continuous optimization.

>>>>

\vspace{-0.3cm}
\paragraph{Occlusion handling in tracking}
Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicitly models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling, on the other hand, is fully 3D, based on physical modeling of object-ray intersections and much more general in determining the probability of a point in space as belonging to an object. While our model can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it has far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.

@@

\vspace{-0.3cm}
\paragraph{Motion segmentation and multibody SFM}
An application for our occlusion modeling is to determine point track associations in scenes with multiple objects. For moving objects, this is within the purview of motion segmentation, which has been approached through algebraic factorization methods \cite{Costeria98,Vidal03,Vidal04}, statistical methods~\cite{Kanatani01,Gruber04,Rao08} and clustering methods~\cite{Yan06,Goh07}. Some recent efforts include robust algebraic segmentation with hybrid perspective constraints \cite{Rao_etal_2010} and spectral clustering with point track spatial affinities \cite{Brox_Malik_2010}. In contrast to our modeling, such methods cannot handle static objects, or dynamic objects with little relative motion.
%\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 
Closer to our application, motion segmentation is also used within multibody SFM frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}. In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.

@@

\vspace{-0.3cm}
\paragraph{3D localization}
One of the vital goals of 3D scene understanding is to localize the 3D objects in complex scenes. 
%For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. 
Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} considers partial object detectors. A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects. In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space and derives unified representations for SFM points and object detection bounding boxes. This makes our model more general, extensible and amenable for continuous optimization.
